Fast Regression of the Tritium Breeding Ratio in Fusion Reactors

### 2020-06-18 paper/results.tex
decrease table row spacing
add back 'computational' after it was mistakenly removed during a merge
minor content and typesetting adjustments
ran spell check, transformed -ise verbs to -ize as per IOP guidelines

Consistent with our expectation, the shortest training times were achieved by
instance-based learning methods (KNN, IDW) that
are trained trivially at the expense of increased lookup complexity later during prediction.
Furthermore, we observe that the majority of tree-based ensemble algorithms also perform
and scale well, unlike RBFs and GPR which appear to behave superlinearly. We note that ANNs,
which are the only family to utilise parallelisation during training, show an
inverse scaling characteristic. We suspect that this effect may be caused
by a constant multi-threading overhead that dominates the training process
on relatively small sets.

@@

In Experiment~4, we aim to create models that yield:
(a)~the best regression performance regardless
of other features, (b)~acceptable performance with the shortest mean
prediction time, or (c)~acceptable performance with the smallest training set.
To this end, we trained 8~surrogates that are presented in~\Fref{fig:reg-performance}
and~\Tref{tbl:exp4-detailed-results}.
Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
Experiments~2 \&~3, we utilised the best-performing hyperparameters.
In pursuit of goal~(a), the best approximator (Model~1,
ANN) achieved~$R^2=\num{0.998}$ and mean prediction
time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
to a standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
with respect to the MC TBR evaluation baseline. Satisfying
goal~(b), the fastest model (Model~2, ANN) achieved~$R^2=\num{0.985}$,
$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
and~$\omega=\num{8659251} \times$.
While these surrogates
were trained on the entire available set of~\num{500000} datapoints, to satisfy
goal~(c) we also trained a more simplified model (Model~4, GBT)
that achieved~$R^2=\num{0.913}$,
$\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
with a set of size only~\num{10000}.

\begin{table*}
	\centering
	\sisetup{round-mode=places,round-precision=3,detect-weight=true,detect-family=true}
	\caption{\label{tbl:exp4-detailed-results}Results of Experiment~4. Here,
		average values and standard deviations are reported over 5~cross-validation folds,
		$|\mathcal{T}|$~denotes cross-validation set size ($\times 10^3$)
		and $\omega$ is a relative speedup with respect to
		$\overline{t}_{\text{eval.}}=\num{7.777049573054314} \pm
		\num{2.8103592103930337} \text{ s}$
		measured in the MC TBR model over~\num{500000} samples.
	The best-performing method(s) under each are highlighted in bold.}
	\setlength\tabcolsep{4pt}
	\begin{indented}
	\item[]
		\scriptsize
		\begin{tabular}{lrrrrrrrr}
		\toprule
		{} & {} & \multicolumn{4}{c}{Regression performance} &
		\multicolumn{3}{c}{Complexity}\\
		\cmidrule(lr){3-6}
		\cmidrule(lr){7-9}
		Model & $|\mathcal{T}|$ & MAE [TBR] & $S$ [TBR] & $R^2$ [rel.] & $R^2_{\text{adj.}}$ [rel.]
						& $\overline{t}_{\text{trn.}}$ [\si{\milli\second}] &
		$\overline{t}_{\text{pred.}}$ [\si{\milli\second}] & $\omega$ [rel.]\\
		\midrule
		\input{tbl/table11}
		\bottomrule
		\end{tabular}
	\end{indented}
\end{table*}

@@

\begin{figure}
	\centering
	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.pdf}
	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and baseline scheme, with 100k initial samples.}
\end{figure}

>>>>

Consistent with our expectation, the shortest training times were achieved by
instance-based learning methods (KNN, IDW) that
are trained trivially at the expense of increased lookup complexity later during prediction.
Furthermore, we observe that the majority of tree-based ensemble algorithms also perform
and scale well, unlike RBFs and GPR which appear to behave superlinearly. We note that ANNs,
which are the only family to utilize parallelisation during training, show an
inverse scaling characteristic. We suspect that this effect may be caused
by a constant multi-threading overhead that dominates the training process
on relatively small sets.

@@

In Experiment~4, we aim to create models that yield:
(a)~the best regression performance regardless
of other features, (b)~acceptable performance with the shortest mean
prediction time, or (c)~acceptable performance with the smallest training set.
To this end, we trained 8~surrogates that are presented in~\Fref{fig:reg-performance}
and~\Tref{tbl:exp4-detailed-results}.
Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
Experiments~2 \&~3, we utilized the best-performing hyperparameters.
In pursuit of goal~(a), the best approximator (Model~1,
ANN) achieved~$R^2=\num{0.998}$ and mean prediction
time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
to a standard error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
with respect to the MC TBR evaluation baseline. Satisfying
goal~(b), the fastest model (Model~2, ANN) achieved~$R^2=\num{0.985}$,
$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
and~$\omega=\num{8659251} \times$.
While these surrogates
were trained on the entire available set of~\num{500000} datapoints, to satisfy
goal~(c) we also trained a more simplified model (Model~4, GBT)
that achieved~$R^2=\num{0.913}$,
$\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
with a set of size only~\num{10000}.

\begin{table*}
	\centering
	\sisetup{round-mode=places,round-precision=3,detect-weight=true,detect-family=true}
	\caption{\label{tbl:exp4-detailed-results}Results of Experiment~4. Here,
		average values and standard deviations are reported over 5~cross-validation folds,
		$|\mathcal{T}|$~denotes cross-validation set size ($\times 10^3$)
		and $\omega$ is a relative speedup with respect to
		$\overline{t}_{\text{eval.}}=\num{7.777049573054314} \pm
		\num{2.8103592103930337} \text{ s}$
		measured in the MC TBR model over~\num{500000} samples.
	The best-performing method(s) under each are highlighted in bold.}
	\setlength\tabcolsep{4pt}
	\renewcommand{\arraystretch}{0.95}
	\begin{indented}
	\item[]
		\scriptsize
		\begin{tabular}{lrrrrrrrr}
		\toprule
		{} & {} & \multicolumn{4}{c}{Regression performance} &
		\multicolumn{3}{c}{Computational complexity}\\
		\cmidrule(lr){3-6}
		\cmidrule(lr){7-9}
		Model & $|\mathcal{T}|$ & MAE [TBR] & $S$ [TBR] & $R^2$ [rel.] & $R^2_{\text{adj.}}$ [rel.]
						& $\overline{t}_{\text{trn.}}$ [\si{\milli\second}] &
		$\overline{t}_{\text{pred.}}$ [\si{\milli\second}] & $\omega$ [rel.]\\
		\midrule
		\input{tbl/table11}
		\bottomrule
		\end{tabular}
	\end{indented}
\end{table*}

@@

\begin{figure}
	\centering
	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.pdf}
	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and
	baseline scheme, with~\num{100000} initial samples.}
\end{figure}
